Deploy

### 2023-12-22 README.Rmd
Transfer ownership

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/v0.5/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=v0.5)
[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
[![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/gesistsa/oolong/branch/v0.5/graph/badge.svg)](https://codecov.io/gh/gesistsa/oolong?branch=v0.5)
[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
[![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
<!-- badges: end -->

### 2023-12-22 deploy_gh.Rmd
Make abstracts_keyatm the 'default' topic model to save space; various fixes for CRAN
Transfer ownership

---
title: "Deploy"
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---

@@

```{r}
library(oolong)
wsi_test <- wsi(abstracts_stm)
wsi_test
```

>>>>

---
title: "Deploy"
output: github_document
author:
  - Chung-hong Chan ^[GESIS]
---

@@

```{r}
library(oolong)
wsi_test <- wsi(abstracts_keyatm)
wsi_test
```
